An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-30 main.tex
added url

\small
\vspace{-10pt}
DOI for the experiment involved in the paper: \url{doi:10.7274/R0C24TCG}

\section*{Acknowledgments}

>>>>

\small
\vspace{-10pt}
DOI for the experiment involved in the paper: \url{doi:10.7274/R0C24TCG}
The detailed description of Athena experiment and how it was run is described in detail at: \url{https://sites.google.com/site/invariantcompatlas/} 
\section*{Acknowledgments}
